MLCommons Earthquake Science Benchmark

### 2022-02-19 paper-capstone-earthquake.tex
fx compile errors

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{format/acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
\usepackage[numbers]{natbib}‎

\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

@@

%% Not sure what's the correct copyright to set in this template...  See the below link for
%% the allowed options in Table 3.  Would this be acmlicensed as we're retaining copyright,
%% but are allowing ACM's usage?  Or are we publishing elsewhere and this should be none?
%% https://www.acm.org/binaries/content/assets/publications/consolidated-tex-template/acmart.pdf#page=18
\setcopyright{none}
%\setcopyright{Apache 2.0}
%\setcopyright{rightsretained}
\copyrightyear{}
%\acmYear{2022}
\acmDOI{}

%\acmConference[T. Buttler, R. Knuuti, J, Kolesar, G. C. Fox,
%  G. von Laszewski, J. Fox, University of Virginia Data Science
%  Capstone 2022]{MLCommons Earthquake Science Benchmark}{Jan. 22 --
%  Aug. 31 2022}{Charlotsville, VA, USA}

@@

%% see http://dl.acm.org/ccs.cfm.
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

@@

@@

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        Section & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidid{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidid{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

{\bf Jake Kolessar}
{is a Graduate Student at the University of Virginia's School of Data Science. He has a background in mechanical engineering and 2 years of experience as a Modeling, Simulation & Analysis Engineer. He has supported the software design and development of modeling capabilities for event simulation products as well as the integration of models into the simulation framework.}

@@

\subsection{Generated List}
\listoftodos{}

@@

>>>>

\PassOptionsToPackage{hyphens}{url}
\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[pdf]{graphviz}
\usepackage{xpatch}
\usepackage{adjustbox}
\usepackage{makecell} 
\usepackage{ifthen}
% \usepackage[numbers]{natbib}‎

%\usepackage[colorlinks = true,
%            linkcolor = blue,
%            urlcolor  = blue,
%            citecolor = blue,
%            anchorcolor = blue]{hyperref}

@@

\setcopyright{none}
%\setcopyright{rightsretained}
\copyrightyear{}
%\acmYear{2022}
\acmDOI{}

@@

\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

@@

\TODO{Fix the classification. See  \url{see http://dl.acm.org/ccs.cfm}}

@@

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        Section & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidia{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidia{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

{\bf Jake Kolessar} {is a Graduate Student at the University of
  Virginia's School of Data Science. He has a background in mechanical
  engineering and 2 years of experience as a Modeling, Simulation and
  Analysis Engineer. He has supported the software design and
  development of modeling capabilities for event simulation products
  as well as the integration of models into the simulation framework.}

@@

\subsection{Generated List}

@@

\listoftodos{}
